Legends for Tables

### 2019-05-12 Manuscript/Tables/table_legends.Rmd
consolidated figure 4 into a table with bin and ir summaries; updated legends

>>>>

**Table 1. Data Summaries.** The average number of genomic bins and corresponding imbalance ratios, across each of the autosomal chromosomes (omitting chromosome 9), stratified by resolution and cell line. The resolution of the Hi-C contact matrix dictated the width of each genomic bin, with lower resolutions corresponding to wider genomic bins.
